API design for machine learning software: experiences from the scikit-learn project

### 2013-08-05 paper.tex
Wording

To facilitate the installation and thus adoption of \sklearn,
the set of external dependencies is kept to a bare minimum:
only Python, NumPy and SciPy are required for a functioning installation.
Binary distributions of these are available for the major platforms.
Visualization functionality depends on Matplotlib \citep{hunter2007matplotlib}
and/or Graphviz \citep{gansner2000},
but neither is required to do machine learning.
When feasible, external libraries are integrated into the codebase.
In particular, \sklearn includes modified versions of \textsf{LIBSVM} and \textsf{LIBLINEAR}
\citep{chang2011libsvm,fan2008}, both written in C{}\verb!++!
and wrapped using Cython modules.

>>>>

To facilitate the installation and thus adoption of \sklearn,
the set of external dependencies is kept to a bare minimum:
only Python, NumPy and SciPy are required for a functioning installation.
Binary distributions of these are available for the major platforms.
Visualization functionality depends on Matplotlib \citep{hunter2007matplotlib}
and/or Graphviz \citep{gansner2000},
however neither is required to do machine learning.
When feasible, external libraries are integrated into the codebase.
In particular, \sklearn includes modified versions of \textsf{LIBSVM} and \textsf{LIBLINEAR}
\citep{chang2011libsvm,fan2008}, both written in C{}\verb!++!
and wrapped using Cython modules.
